SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-04-17 intro.tex
removed an extra period '.'

Figure~\ref{Fig:Motivation} illustrates the above scenario.  Here we
consider a state-of-the-art. lookahead prefetcher -- SPP~\cite{SPP}.
Lookahead prefetchers such as SPP provide a mechanism to speculate an
arbitrary number of references ahead of the initial triggering miss.
In SPP, a throttling confidence threshold is then used to ensure that
the lookahead stops when confidence falls too low to ensure that
prefetches are accurate.  In the figure, we iteratively re-tuned 
this threshold to allow the prefetcher to lookahead a fixed
depth from 7 to 15. The figure depicts the behavior 
of the {\tt 603.bwaves\_s} SPEC CPU 2017 benchmark. The IPC, the 
total number of prefetches issued by the prefetcher (TOTAL\_PF), 
and the actual useful predictions (GOOD\_PF), all have been normalized 
to lookahead depth 7. As the lookahead
depth increases, so do useful prefetches, and hence coverage. This
coverage, however, comes at the cost of total prefetches increasing at
an even higher rate. This leads to cache pollution and bandwidth
contention, and leads to a reduction in IPC.  
%Similar behavior was observed in 12 other SPEC CPU 2017 benchmarks.

>>>>

Figure~\ref{Fig:Motivation} illustrates the above scenario.  Here we
consider a state-of-the-art lookahead prefetcher -- SPP~\cite{SPP}.
Lookahead prefetchers such as SPP provide a mechanism to speculate an
arbitrary number of references ahead of the initial triggering access.
In SPP, a throttling confidence threshold is then used to ensure that
the lookahead stops when confidence falls too low to ensure that
prefetches are accurate.  In the figure, we iteratively re-tuned 
this threshold to allow the prefetcher to lookahead a fixed
depth from 7 to 15. The figure depicts the behavior 
of the {\tt 603.bwaves\_s} SPEC CPU 2017 benchmark. The IPC, the 
total number of prefetches issued by the prefetcher (TOTAL\_PF), 
and the actual useful predictions (GOOD\_PF), all have been normalized 
to lookahead depth 7. As the lookahead
depth increases, so do useful prefetches, and hence coverage. This
coverage, however, comes at the cost of total prefetches increasing at
an even higher rate. This leads to cache pollution and bandwidth
contention, and leads to a reduction in IPC.  
%Similar behavior was observed in 12 other SPEC CPU 2017 benchmarks.
